---
libtitle: "Week5Problems"
author: "Ashley"
date: "5/9/2020"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## 10.5 Problems

1. How can you tell if an object is a tibble? (Hint: try printing mtcars, which is a regular data frame).
    + If you print a tibble it is labled 'A tibbble' where as a regular data frame is not labeled
    + tibble prints the first ten rows whereas the data frame prints the whole set 
  
```{r}
print(mtcars)
print(diamonds)
```

2. Compare and contrast the following operations on a data.frame and equivalent tibble. What is different? Why might the default data frame behaviours cause you frustration?
    + **I am not sure what is going on** 
```{r}
df <- data.frame(abc = 1, xyz = "a")
df$x
df[, "xyz"]
df[, c("abc", "xyz")]
```

3. Practice referring to non-syntactic names in the following data frame by:
    + Extracting the variable called 1.
    + Plotting a scatterplot of 1 vs 2.
    + Creating a new column called 3 which is 2 divided by 1.
    + Renaming the columns to one, two and three.
```{r}
annoying <- tibble(
  `1` = 1:10,
  `2` = `1` * 2 + rnorm(length(`1`))
)

annoying$'1'

annoying %>% ggplot(aes(x=`1`,y=`2`)) + geom_point()

transmute(annoying, 
            one = `1`,
            two = `2`,
             three = `2` / `1` )
  
```

**I combined 3 and 4 because I couldn't figure out how to rename**

4. What does tibble::enframe() do? When might you use it? 
  + Converts vectors into tibbles 
    + **I am not sure when you would use it**
  
```{r}
enframe(c(a = 5, b = 7))
```

## 11.2.2 Problems

1. What function would you use to read a file where fields were separated with
“|”?
```{r}

read_delim("1 | 2 | 3 \n a | b | c", delim ="|")
``` 
4. Sometimes strings in a CSV file contain commas. To prevent them from causing problems they need to be surrounded by a quoting character, like " or '. By default, read_csv() assumes that the quoting character will be ". What argument to read_csv() do you need to specify to read the following text into a data frame?
    + **I am not sure how to group 'a, b' into its own column**

```{r}
read_delim("x,y\n1,'a,b'",delim = "'")
```

5. Identify what is wrong with each of the following inline CSV files. What happens when you run the code?

```{r}
read_csv("a,b\n1,2,3\n4,5,6")
## There are only two columns defined, but there are three values for each row, the last values for each row are dropped

read_csv("a,b,c\n1,2\n1,2,3,4")
## There are only two values in the first row so there is a "NA" in column c, and the extra value in the second row is dropped

read_csv("a,b\n\"1")
## An extra "? The b column is parsed as a character isnetead of a number and there is a NA in the second column. 

read_csv("a,b\n1,2\na,b")
## Confusing quotation marks

read_csv("a;b\n1;3")
## Only one column and one variable described 

```

## 11.3.5 Problems
1. What are the most important arguments to locale()?
    + You can define what you used as a decimal point in your data locale = locale(decimal_mark = ",")
    + You can define grouping marks  locale = locale(grouping_mark = ".")
    + For different languages  locale = locale(encoding = ",")
  
2. What happens if you try and set decimal_mark and grouping_mark to the same character? 
     + There is an error in the locale and it says they must be different 
```{r}
## parse_number("123.456.789", locale = locale(grouping_mark = ".", decimal_mark = "."))
```
  + What happens to the default value of grouping_mark when you set decimal_mark to “,”? 
    + The grouping mark becomes "."
```{r}
 parse_number("123.456.789", locale = locale(decimal_mark = ","))
```

  + What happens to the default value of decimal_mark when you set the grouping_mark to “.”? 
    + The decimal mark becomes ","
```{r}
parse_number("123.456.789", locale = locale(grouping_mark = "."))
parse_number("123,456,789", locale =locale(grouping_mark = "."))
```

3. I didn’t discuss the date_format and time_format options to locale(). What do they do? Construct an example that shows when they might be useful.
    + They define how R parses date and time, you can change it to different countries
  
```{r}
parse_date("1 janvier 2015", "%d %B %Y", locale = locale("fr"))

```

7. Generate the correct format string to parse each of the following dates and times:

```{r}
d1 <- "January 1, 2010"
parse_date(d1, "%B %d, %Y")

d2 <- "2015-Mar-07"
parse_date(d2, "%Y-%b-%d")

d3 <- "06-Jun-2017"
parse_date(d3, "%d-%b-%Y")

d4 <- c("August 19 (2015)", "July 1 (2015)")
parse_date(d4, "%B %d (%Y)")

d5 <- "12/30/14" # Dec 30, 2014
parse_date(d5, "%m/%d/%y")

t1 <- "1705"
parse_time(t1, "%H%M")

t2 <- "11:15:10.12 PM"
parse_time(t2, "%H:%M:%S %p")
```
