---
title: "Week6Problems"
author: "Ashley"
date: "5/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
```

## 12.2.1 Problems 
2. Compute the rate for table2, and table4a + table4b. You will need to perform four operations:
    - Extract the number of TB cases per country per year.
    - Extract the matching population per country per year.
    - Divide cases by population, and multiply by 10000.
    - Store back in the appropriate place.
    - Which representation is easiest to work with? Which is hardest? Why?
      - The two separate tables were easier to work with because the population and TB cases per year are separated
```{r}

 filter(table2, type == "cases") 
 filter(table2, type == "population") 
```
```{r}
cases <- select (table4a, '1999', '2000')
population <- select(table4b, '1999', '2000')
rates <- (cases/population)*(10000)
rate <- tibble (rates)

new <- tibble(
  country = table4a$country,
  '1999' = rates$'1999',
  '2000' = rates$'2000'
      )

print(new)
```

3. Recreate the plot showing change in cases over time using table2 instead of table1. What do you need to do first?

```{r}
table2 %>%
  filter(type == "cases") %>%
  ggplot(aes(year, count)) +
  geom_line(aes(group = country, color = country))
  
```

## 12.3.3 Problems
1. Why are pivot_longer() and pivot_wider() not perfectly symmetrical?

```{r}
stocks <- tibble(
  year   = c(2015, 2015, 2016, 2016),
  half  = c(   1,    2,     1,    2),
  return = c(1.88, 0.59, 0.92, 0.17)
)

stocks %>% 
  pivot_wider(names_from = year, values_from = return) 
```

```{r}
stocks <- tibble(
  year   = c(2015, 2015, 2016, 2016),
  half  = c(   1,    2,     1,    2),
  return = c(1.88, 0.59, 0.92, 0.17)
)

stocks %>% 
  pivot_wider(names_from = year, values_from = return) %>% 
  pivot_longer(`2015`:`2016`, names_to = "year", values_to = "return")
```
    - pivot_wider creates separate columns for each year while pivot_longer creates a year column with both the separate years
    - pivot_longer() has a names_ptype argument, e.g. names_ptype = list(year = double()). What does it do?
    - I think it converts the year to a number instead of a character 

2. Why does this code fail?
```{r}
##table4a %>% 
  ##pivot_longer(c(1999, 2000), names_to = "year", values_to = "cases")
#> Error: Can't subset columns that don't exist.
#> ✖ The locations 1999 and 2000 don't exist.
#> ℹ There are only 3 columns.
```
    - There are no backticks around the years

3. What would happen if you widen this table? Why? How could you add a new column to uniquely identify each value?
    - If you try to widen this table Phillip Woods would receive two ages (?)
    
```{r}
people <- tribble(
  ~name,             ~names,  ~values,
  #-----------------|--------|------
  "Phillip Woods",   "age",       45,
  "Phillip Woods",   "height",   186,
  "Phillip Woods",   "age",       50,
  "Jessica Cordero", "age",       37,
  "Jessica Cordero", "height",   156
  

)%>%
pivot_wider(names_from= names, values_from= values)
print(people)
```

4. Tidy the simple tibble below. Do you need to make it wider or longer? What are the variables?
    - We can make it longer 
```{r}
preg <- tribble(
  ~pregnant, ~male, ~female,
  "yes",     NA,    10,
  "no",      20,    12
)%>% print() %>%
  pivot_longer(c('male', 'female'), names_to = "gender", values_to = "count")
print(preg)
```

## 12.4.3 Problems
1. What do the extra and fill arguments do in separate()? Experiment with the various options for the following two toy datasets.
    - extra controls character vectors and drops or splits apart extra values (warn drops extra values)
    - fill controls chracter vectors when there are not enough pieces (warn fills missing values from the right)

```{r}
tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three"), extra = "warn")

tibble(x = c("a,b,c", "d,e", "f,g,i")) %>% 
  separate(x, c("one", "two", "three"), fill = "right")
```

2. Both unite() and separate() have a remove argument. What does it do? Why would you set it to FALSE?
    - Remove eliminates the original columns you joined with unite() and keeps the column you separated 
      - You would set it to FALSE if you want to see what values the new united column came from and what the separated columns came from
     
```{r}
table5 %>% 
  unite(new, century, year, remove = FALSE)

table3 %>% 
  separate(rate, into = c("cases", "population"), remove=FALSE)
```

3. Compare and contrast separate() and extract(). Why are there three variations of separation (by position, by separator, and with groups), but only one unite?
    - separate() splits one column into two while extract() turns each group into a column 
    - Both create columns based on existing ones
    - You can separate things in many different ways but to unite something an underscore is immediately places between each value and you can remove this in any way you want later on  

## 12.6.1 Problems
1. I claimed that iso2 and iso3 were redundant with country. Confirm this claim.
    - I'm not sure how to do this 

2. For each country, year, and sex compute the total number of cases of TB. Make an informative visualisation of the data.
```{r}
who1 <- who %>% 
  pivot_longer(
    cols = new_sp_m014:newrel_f65, 
    names_to = "key", 
    values_to = "cases", 
    values_drop_na = TRUE
  )
who2 <- who1 %>% 
  mutate(names_from = stringr::str_replace(key, "newrel", "new_rel"))
who3 <- who2 %>% 
  separate(key, c("new", "type", "sexage"), sep = "_")
who3 %>% 
  count(new)
who4 <- who3 %>% 
  select(-new, -iso2, -iso3)
who5 <- who4 %>% 
  separate(sexage, c("sex", "age"), sep = 1)

who5 %>%
  ggplot(
    aes(x = year, y = cases, color = sex)
    ) + 
   geom_smooth()

```

