---
title: "Week3Problems"
author: "Ashley"
date: "5/1/2020"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(nycflights13)
```

## 4.4 Exercises

1. Why is this code wrong? 
    - The second line of code spelled 'variable' with a '1' for the 'i'
    
2. Tweaked code:
    - Changed 'dota' to 'data'
    - Changed 'cyl = 8' to 'cyl == 8'
    - Changed 'diamond' to 'diamonds' 
    
```{r}

ggplot(data=mpg)+geom_point(mapping = aes(x=displ,y=hwy))

filter(mpg, cyl == 8)
filter(diamonds, carat > 3)
```

## 5.2.4 Exercises

1. Find all flights that:
    - Had an arrival delay of two or more hours
```{r }
filter(flights, arr_delay >= 120)
```

    - Departed in the summer (July, August, September)
```{r}
filter(flights, month == 7|  month == 8| month == 9)
```

    - Arrived more than two hours late, but did not depart late
```{r}
filter(flights, arr_delay >= 120 & dep_delay ==0)
```

    - Departed between midnight and 6am
```{r}
filter(flights,dep_time>=0 & dep_time <=0600)
```

2. Simplifying code with between()

```{r}
filter(flights, between(dep_time,0600,2359))
```

3. How many flights have a missing dep_time? What other variables are missing? What might these rows represent?
    - There are 8225 flights with a missing departure time
    - arr_time, air_time, and dep_delay are also missing
    
```{r}
filter(flights, is.na(dep_time))
```

## 5.3.1 Exercises

1. Use arrange() to sort all NA values to the start 
```{r}
arrange(flights, desc(is.na(dep_time)), dep_time)
```

2. Find the most delayed flights and the flights that left the earliest. 
```{r}
arrange(flights,dep_delay)
arrange(flights, desc(dep_delay))
```

3. Find the fastest flights
```{r}
arrange(flights,air_time)
```

4. Which flights travelled the furtherst? Which flights travelled the shortest?
```{r}
arrange(flights,desc(distance))
arrange(flights, distance)
```

## 5.4.1 Exercises

1. Ways to select dep_time, dep_delay, arr_time, and arr_delay from flights.
```{r}
select(flights, dep_time, dep_delay, arr_time, arr_delay)
select(flights, starts_with("arr"), starts_with("dep"))

x <- c("dep_time","dep_delay","arr_time","arr_delay")
select(flights,one_of(x))

```

2. What happens if you include the name of a variable multiple times in a select() call?
    - The variable is only shown once
``` {r}
select(flights,dep_time,dep_time)
```

3. What does the one_of() function do? Why might it be helpful in conjunction with this vector?
    - One_of allows you to select all the elements described in one variable
```{r}
vars <- c("year", "month", "day", "dep_delay", "arr_delay")
select(flights,one_of(vars))
```

4. Does the result of running the following code surprise you? How do the select helpers deal with case by default? How can you change that default?
    - Select ignores case differences
```{r}
select(flights, contains("TIME"))
```

## 5.5.2 Exercises
1. Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.
```{r}
departures <- select(flights, dep_time,sched_dep_time)

mutate(departures,
       dep_time_min = (dep_time%/%100)*60 + (dep_time%%100),
       sched_dep_time_min = (sched_dep_time%/%100)*60 + (sched_dep_time%%100)
)
```

2. Compare air_time with arr_time - dep_time. What do you expect to see? What do you see? What do you need to do to fix it?
    - I expect them to be equal 
    - **You need to convert the arrival and departure time to minute. Why isn't air_time the difference in minutes between the two?**
```{r}
times <- select(flights, dep_time,arr_time, air_time)
times
transmute(times,
       dep_time_min = (dep_time%/%100)*60 + (dep_time%%100),
       arr_time_min = (arr_time%/%100)*60 + (arr_time%%100),
       air_time_new = arr_time_min - dep_time_min)

```

3. Compare dep_time, sched_dep_time, and dep_delay. How would you expect those three numbers to be related?
    - Expect dep_delay = sched_dep_time (in min) - dep_time (in min)
  

4. **Find the 10 most delayed flights using a ranking function. How do you want to handle ties? Carefully read the documentation for min_rank().**

```
x<- select(flights,arr_delay)
min_rank(desc(x))
```

5. What does 1:3 + 1:10 return? Why?
    - It returned 2, 4, 6, 5, 7, 9, 8, 10, 12, 11 because the 1:3 gets cycled as many times as it needs to complete the operation 

## Exercise 5.6.7
5. Which carrier has the worst delays? Challenge: can you disentangle the effects of bad airports vs. bad carriers? Why/why not? (Hint: think about flights %>% group_by(carrier, dest) %>% summarise(n()))
    **What does %>% do?**
    
    
    
    